---
title: "Decision-maker survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

# Loading packages
```{r include=FALSE}
library(psych)
library(qwraps2)
library(DescTools)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(dplyr)
library(ggplot2)
library(magrittr)
library(tidyr)
library(stargazer)
library(jtools)
library(estimatr)
library(tidyverse)
library(haven)
library(modelsummary)
library(lmtest)
library(sandwich)
```


Loading the data set:
```{r}
data <-  read.csv("decision_maker_survey_data.csv", head = TRUE, sep = ",")
data$treatment <- ifelse((data$info_group == "Treatment"), 1, 0)

data$prior_belief_platforms_win <- Winsorize(data$prior_belief_platforms, minval = NULL, maxval = NULL,
                                       probs = c(0.00, 0.95), na.rm = TRUE, type = 7) 
data$posterior_belief_win <- Winsorize(data$posterior_belief, minval = NULL, maxval = NULL,
                                            probs = c(0.00, 0.95), na.rm = TRUE, type = 7)
```


```{r}
control_set = ~. + full_time_employee + 
                     final_marketing + 
                     duration_of_role + 
                     num_employees + factor(industry) + US_HQ +
                     prior_companies_1 + prior_belief_platforms_win + 
                     uses_digital_ads + 
                     consumer_info_demand_yes + requests_full_ad_check 
```


# Treatment and Control:
```{r}
data_C <- data[data$info_group == "Control", ]
n_C <- nrow(data_C)
print(n_C)

data_T <- data[data$info_group == "Treatment", ]
n_T <- nrow(data_T)
print(n_T)

n_T + n_C
nrow(data)
```

# Prior own company belief:
```{r}
data_own_company_yes <-  data[data$prior_own_company == "Yes", ]
n_own_company_yes <- nrow(data_own_company_yes)
print(n_own_company_yes)

data_own_company_no <-  data[data$prior_own_company == "No", ]
n_own_company_no <- nrow(data_own_company_no)
print(n_own_company_no)
```




############################################### FULL DATA ########################################################


# Posterior beliefs: 
```{r}
posterior_beliefs_reg <- lm(update(posterior_belief_win ~ treatment, control_set), data = data)  
tab_model(posterior_beliefs_reg)

posterior_beliefs_coeftest_all <- coeftest(posterior_beliefs_reg, vcov = vcovHC(posterior_beliefs_reg, type = 'HC1'))
posterior_beliefs_coeftest_all
```

```{r}
posterior_beliefs_reg <- lm(update(posterior_belief_win ~ treatment, control_set), data = data_own_company_yes) 
tab_model(posterior_beliefs_reg)

posterior_beliefs_coeftest_yes <- coeftest(posterior_beliefs_reg, vcov = vcovHC(posterior_beliefs_reg, type = 'HC1'))
posterior_beliefs_coeftest_yes
```

```{r}
posterior_beliefs_reg <- lm(update(posterior_belief_win ~ treatment, control_set), data = data_own_company_no)
tab_model(posterior_beliefs_reg)
summary(posterior_beliefs_reg)

posterior_beliefs_coeftest_no <- coeftest(posterior_beliefs_reg, vcov = vcovHC(posterior_beliefs_reg, type = 'HC1'))
posterior_beliefs_coeftest_no
```


# Platform solution demand:
```{r}
platform_choice_reg <- lm(update(platform_choice_misinfo ~ treatment, control_set), data = data) 
tab_model(platform_choice_reg)

platform_choice_o1_coeftest_all <- coeftest(platform_choice_reg, vcov = vcovHC(platform_choice_reg, type = 'HC1'))
platform_choice_o1_coeftest_all
```

```{r}
platform_choice_reg <- lm(update(platform_choice_misinfo ~ treatment, control_set), data = data_own_company_yes)
tab_model(platform_choice_reg)

platform_choice_o1_coeftest_yes <- coeftest(platform_choice_reg, vcov = vcovHC(platform_choice_reg, type = 'HC1'))
platform_choice_o1_coeftest_yes
```

```{r}
platform_choice_reg <- lm(update(platform_choice_misinfo ~ treatment, control_set), data = data_own_company_no)
tab_model(platform_choice_reg)

platform_choice_o1_coeftest_no <- coeftest(platform_choice_reg, vcov = vcovHC(platform_choice_reg, type = 'HC1'))
platform_choice_o1_coeftest_no
```


```{r}
library("texreg")
texreg(list(posterior_beliefs_coeftest_all,
            posterior_beliefs_coeftest_yes, 
            posterior_beliefs_coeftest_no,
            platform_choice_o1_coeftest_all,
            platform_choice_o1_coeftest_yes,
            platform_choice_o1_coeftest_no), 
       stars = c(0.01, 0.05, 0.10))
```



########################################### SUBSAMPLE ANALYSIS #####################################################

# Selecting sub-samples based on own company belief confidence:
```{r}
data_own_company_uncertain_no <-  data_own_company_no[(data_own_company_no$prior_own_company_c == "Very unsure") |
                                                      (data_own_company_no$prior_own_company_c == "Unsure"), ]
n_own_company_uncertain_no <- nrow(data_own_company_uncertain_no)
print("N (data_own_company_uncertain_no): ")
print(n_own_company_uncertain_no)


data_own_company_certain_no <-  data_own_company_no[(data_own_company_no$prior_own_company_c == "Somewhat sure") | 
                                                 (data_own_company_no$prior_own_company_c == "Sure") | 
                                                 (data_own_company_no$prior_own_company_c == "Very sure"), ]
n_own_company_certain_no <- nrow(data_own_company_certain_no)
print("N (data_own_company_certain_no): ")
print(n_own_company_certain_no)
```

# Posterior beliefs: 
```{r}
posterior_beliefs_reg <- lm(update(posterior_belief_win ~ treatment, control_set), 
                            data = data_own_company_certain_no)
tab_model(posterior_beliefs_reg)

posterior_beliefs_certain_no_coeftest <- coeftest(posterior_beliefs_reg, 
                                                  vcov = vcovHC(posterior_beliefs_reg, type = 'HC1'))
posterior_beliefs_certain_no_coeftest
```


```{r}
posterior_beliefs_reg <- lm(update(posterior_belief_win ~ treatment, control_set), 
                            data = data_own_company_uncertain_no)
tab_model(posterior_beliefs_reg)

posterior_beliefs_uncertain_no_coeftest <- coeftest(posterior_beliefs_reg, 
                                                    vcov = vcovHC(posterior_beliefs_reg, type = 'HC1'))
posterior_beliefs_uncertain_no_coeftest
```


# Platform solution demand:
```{r}
platform_choice_reg <- lm(update(platform_choice_misinfo ~ treatment, control_set), 
                          data = data_own_company_certain_no)
tab_model(platform_choice_reg)

platform_choice_o1_coeftest_certain_no <- coeftest(platform_choice_reg, 
                                                   vcov = vcovHC(platform_choice_reg, type = 'HC1'))
platform_choice_o1_coeftest_certain_no
```
`

```{r}
platform_choice_reg <- lm(update(platform_choice_misinfo ~ treatment, control_set), 
                          data = data_own_company_uncertain_no)
tab_model(platform_choice_reg)

platform_choice_o1_coeftest_uncertain_no <- coeftest(platform_choice_reg, 
                                                     vcov = vcovHC(platform_choice_reg, type = 'HC1'))
platform_choice_o1_coeftest_uncertain_no
```



```{r}
library("texreg")
texreg(list(posterior_beliefs_certain_no_coeftest,
            posterior_beliefs_uncertain_no_coeftest,
            platform_choice_o1_coeftest_certain_no,
            platform_choice_o1_coeftest_uncertain_no), 
       stars = c(0.01, 0.05, 0.10))
```


########################################### SUPPLEMENTARY ANALYSIS #####################################################


# GDI donation:
```{r}
donation_GDI_reg <- lm(update(donation_GDI ~ treatment, control_set), data = data)
tab_model(donation_GDI_reg)

donation_GDI_all_coeftest <- coeftest(donation_GDI_reg, vcov = vcovHC(donation_GDI_reg, type = 'HC1'))
donation_GDI_all_coeftest
```

```{r}
donation_GDI_reg <- lm(update(donation_GDI ~ treatment, control_set), data = data_own_company_no)
tab_model(donation_GDI_reg)

donation_GDI_no_coeftest <- coeftest(donation_GDI_reg, vcov = vcovHC(donation_GDI_reg, type = 'HC1'))
donation_GDI_no_coeftest
```

```{r}
donation_GDI_reg <- lm(update(donation_GDI ~ treatment, control_set), data = data_own_company_certain_no)
tab_model(donation_GDI_reg)

donation_GDI_certain_no_coeftest <- coeftest(donation_GDI_reg, vcov = vcovHC(donation_GDI_reg, type = 'HC1'))
donation_GDI_certain_no_coeftest
```

```{r}
donation_GDI_reg <- lm(update(donation_GDI ~ treatment, control_set), data = data_own_company_uncertain_no)
tab_model(donation_GDI_reg)

donation_GDI_uncertain_no_coeftest <- coeftest(donation_GDI_reg, vcov = vcovHC(donation_GDI_reg, type = 'HC1'))
donation_GDI_uncertain_no_coeftest
```


```{r}
library("texreg")
texreg(list(
            donation_GDI_all_coeftest,
            donation_GDI_no_coeftest, 
            donation_GDI_certain_no_coeftest, 
            donation_GDI_uncertain_no_coeftest), 
       stars = c(0.01, 0.05, 0.10))
```


# Setting the dataset we want to the sub-sample of participants in managerial and executive roles:
```{r}
data_DM <- data[data$DM == 1, ] 
n_DM <- nrow(data_DM)
print(n_DM)
data <- data_DM
```
